Fifteen years of decentralization attempts

### 2014-03-24 paper.tex
typo fixes round 3

			Unless hidden services are used, content travels unencrypted through a Tor exit node. Users running a Tor exit node could be held responsible for distributing illegal content. The possibility of being seen as the originator of illegal content refrains users from running an exit node. A possible solution could be to filter the illegal content from the legal content. While content filtering could be a possible solution, it is an open question whether filtering is in line with the principles of Tor and the internet.

@@

		Moving this system to a non peer-to-peer base is difficult: Dingledine et al. stated that this is indeed still an open problem. With decentralized systems, there is no central directory server to tell a new node where to locate neighbors. Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} are decentralized but they do suffer from performance issues.

	\subsection{Key exchange}
		With a decentralized network, using a centralized authority for managing the keys is not possible. This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them. Diffie-Hellman is a very popular algorithm for exchanging keys between two parties. It is used in the circuit creation in Onion Routing (see section \ref{ss:tor_circuit}) for example. However, it is possible for an adversary to manipulate with the keys send between two parties, making the protocol vulnerable to a man-in-the-middle attack. This weakness makes it possible for an adversary to decrypt all messages sent between the two parties.

@@

		Instead of the Directory Servers, it uses a DHT and a new Neighbourhood Authority (NA). The DHT is a combination of Kademlia DHT and Myrmic DHT. Kademlia DHT was chosen because it is already widely used and it has proven itself for a large number of users.

@@

	\subsection{Anonymizing Peer-to-Peer Proxy}
		Anothe proposed decentralized, anonymizing overlay network is Anonymizing Peer-to-Peer Proxy (AP3) \cite{mislove2004ap3} which makes cooperative, decentralized anonymous communication possible. The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms. Users are able to send and receive unicast, multicast and anycast messages anonymously. The strategy that AP3 is using for message delivery is similar to that of Tarzan: it relies on a network of peers to forward messages. A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.

@@

	\begin{itemize}
		\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
		\item{Public implementation:} For each network we will explain whether a public implementation is available.
		\item{Used in practice:} Is the network used in practice?
		\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
		\item{Unlinkability:} Does the network hide the identities of the sender and/or receiver?
	\end{itemize}

>>>>

			Unless hidden services are used, content travels unencrypted through a Tor exit node. Users running a Tor exit node could be held responsible for distributing illegal content. The possibility of being seen as the originator of illegal content refrains users from running an exit node. A possible solution could be to filter the illegal content from the legal content. While content filtering could be a possible solution, it is an open question whether filtering is in line with the principles of Tor and the internet. We think however that filtering the content on Tor could make more users run an exit node and thus improve the quality of the network.

@@

		Moving this system to a peer-to-peer base is difficult: Dingledine et al. stated that this is indeed still an open problem. With decentralized systems, there is no central directory server to tell a new node where to locate neighbors. Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} are decentralized but they do suffer from performance issues.

	\subsection{Key exchange}
		With a decentralized network, using a centralized authority for managing the keys is not possible. This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them. Diffie-Hellman is a very popular algorithm for exchanging keys between two parties. It is used in the circuit creation in Onion Routing (see section \ref{ss:tor_circuit}) for example. However, it is possible for an adversary to manipulate the keys send between two parties, making the protocol vulnerable to a man-in-the-middle attack. This weakness makes it possible for an adversary to decrypt all messages sent between the two parties.

@@

		Instead of the Directory Servers, it uses a DHT and a new Neighbourhood Authority. The DHT is a combination of Kademlia DHT and Myrmic DHT. Kademlia DHT was chosen because it is already widely used and it has proven itself for a large number of users.

@@

	\subsection{Other decentralized systems}
		Some other decentralized peer-to-peer systems has been developed, focussing on anonymity. An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) \cite{mislove2004ap3} which makes cooperative, decentralized anonymous communication possible. The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms. Users are able to send and receive unicast, multicast and anycast messages anonymously. The strategy that AP3 is using for message delivery is similar to that of Tarzan: it relies on a network of peers to forward messages. A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.

@@

	\begin{itemize}
		\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
		\item{Public implementation:} For each network we will explain whether a public implementation is available.
		\item{Used in practice:} Is the network used in practice?
		\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
		\item{Anonymity:} Does the network hide the identities of the sender and/or receiver?
	\end{itemize}
